Modeling browser-based evolutionary computation systems

### 2015-02-05 modeling-volunteer-computing-evopar2015.tex
Paper I didn't start or finish

\documentclass{svmult}

\usepackage{mathptmx,helvet,courier,graphicx,multicol}

@@

\title*{Low or no cost distributed evolutionary computation}
\author{Juan J. Merelo-Guervós}
\institute{GeNeura Group (\url{http://geneura.wordpress.com}), Department of Computer Architecture (\url{http://atc.ugr.es}) and CITIC (\url{http://citic.ugr.es}), University of Granada (Spain) (\url{http://www.ugr.es})}

@@

\abstract{From the era of big science we are back to the "do it yourself", where you do not have any money to buy clusters or subscribe to grids but still have algorithms that crave many computing nodes and need them to measure scalability. Fortunately, this coincides with the era of big data, cloud computing, and browsers that include JavaScript virtual machines. Those are the reasons why this talk will focus on two different aspects of volunteer or freeriding computing: first, the pragmatic: where to find those resources, which ones can be used, what kind of support you have to give them; and then, the theoretical: how evolutionary algorithms can be adapted to a environment in which nodes come and go, have different computing capabilities and operate in complete asynchrony of each other.}

@@

\bibliographystyle{unsrt}
\bibliography{geneura}

>>>>

\documentclass[a4paper]{article}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx,epsfig}
\usepackage{listings}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[affil-it]{authblk}

%%%%

\usepackage{color}
\usepackage{alltt}
\usepackage{verbatim}
\usepackage{url}

\usepackage{url}

@@

\title{Modeling browser-based evolutionary computation systems}
%\author{Juan J. Merelo-Guervós}
\author{Som E. One}
\affil{Somewhere Institute}

@@

\begin{abstract}
From the era of big science we are back to the "do it yourself", where
you do not have any money to buy clusters or subscribe to grids but
still have algorithms that crave many computing nodes and need them to
measure scalability. Fortunately, this coincides with the era of big
data, cloud computing, and browsers that include JavaScript virtual
machines. Those are the reasons why this talk will focus on two
different aspects of volunteer or freeriding computing: first, the
pragmatic: where to find those resources, which ones can be used, what
kind of support you have to give them; and then, the theoretical: how
evolutionary algorithms can be adapted to a environment in which nodes
come and go, have different computing capabilities and operate in
complete asynchrony of each other. 
\end{abstract}

@@

\bibliographystyle{splncs}
\bibliography{geneura,volunteer}
